Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-14 paper/paper.tex
Added content to Windows Vista under data sources

\section{Data Sources}
The choice of dataset is extremely important, especially when doing software defect prediction research. Datasets should be representative of actual software projects and should ideally be accessible to the public so the results can be re-tested and verified by others. Within the referenced papers, we found a variety of data sources which we feel need to be discussed. Primarily, we found open-source datasets, NASA datasets, and Windows Vista datasets. We will discuss each along with some reasons why they may have been chosen.
\subsection{Open-source}
\subsection{NASA}
A few papers (Zheng \cite{zheng2010}...) used datasets from NASA. Among them were KC1, used for storage management, KC2, used for scientific data processing, CM1, used for NASA spacecraft instruments, and PC1, used for flight software.

@@

NASA datasets are publicly available. Researchers can more easily verify the results obtained in a study. Also, since these datasets are static, they can be used as a baseline to compare the results from a newly created model against those from other studies.
\subsection{Windows Vista}

>>>>

\section{Data Sources}
The choice of dataset is extremely important, especially when doing software defect prediction research. Datasets should be representative of actual software projects and should ideally be accessible to the public so the results can be re-tested and verified by others. Within the referenced papers, we found a variety of data sources which we feel need to be discussed. Primarily, we found open-source datasets, NASA datasets, and Windows Vista datasets. We will discuss each along with some reasons why they may have been chosen.
\subsection{Open-source}

\subsection{NASA}
A few papers (Zheng \cite{zheng2010}...) used datasets from NASA. Among them were KC1, used for storage management, KC2, used for scientific data processing, CM1, used for NASA spacecraft instruments, and PC1, used for flight software.

@@

NASA datasets are publicly available. Researchers can more easily verify the results obtained in a study. Also, since these datasets are static, they can be used as a baseline to compare the results from a newly created model against those from other studies.
\subsection{Windows Vista}
Two of the referenced papers (Bird et al \cite{Bird} and Nagappan et al \cite{Nagappan}) use data from Windows Vista. Neither paper tests a fault prediction model using Vista test data. Instead, the first paper examined how different development teams worked together within Microsoft and the second paper examined Microsoft's organizational structure. Two of the three authors of the second paper are associated with Microsoft Research.

But why was Windows Vista chosen? Windows in general is a widely used operating system which contains many lines of code. Windows is also known for being vulnerable without frequent patching and antivirus software. Windows Vista may have been the latest version of Windows at the time of both papers, but Vista is also known as a slow and buggy release. Maybe the authors intended to show that Vista did not contain an unusually high number of bugs compared to other releases, or maybe they just wanted to choose a Microsoft product that was well-known, whether for good or bad.
